### 2025-09-22 Doctor_Paper_Modification/chapters/publications.tex
paper update

\begin{enumerate}
\item XU X H, XIE J L, ZHANG L F, et al. Improvement of transmittance using groove structured surface for microwave imaging diagnostics in tokamak plasmas [J]. Int Conf Infra Milli, 2020.
\item HAN D Q, XIE J L, HUSSAIN A, Xu X H,et al. In situ relative self-dependent calibration of electron cyclotron emission imaging via shape matching [J]. Review of Scientific Instruments, 2018, 89(10).
\item GAO B X, XIE J L, ZHAO Z L, Xu X H,et al. Diagnostic capacity of electron cyclotron emission imaging system with continuous large observation area on EAST tokamak [J]. Review of Scientific Instruments, 2018, 89(9).
\item
LIAO W, GAO F, XU X, et al. Bench test of microwave imaging reflectometry system for EAST tokamak [J]. Journal of Instrumentation, 2020, 15(03): C03036.
\item
高飞雪, 刘贤子, 渠承明,徐新航, et al. EAST 装置微波反射成像系统光学性能评测 [J]. 核聚变与等离子体物理, 2022, 42(2): 187.
\end{enumerate}

@@

\begin{enumerate}
\item Xu Xinhang,Xie Jinlin ,et al.Constraining Electron Energy in static electric Field via the Anomalous Doppler Resonant with External Electromagnetic Waves.
\item Xu Xinhang,Xie Jinlin ,et al.Trapping analysis of a magnetic electron by a circularly polarized electromagnetic wave in static electric field.
\end{enumerate}

>>>>

\begin{enumerate}
\item XU X H, XIE J L, ZHANG L F, et al. Improvement of transmittance using groove structured surface for microwave imaging diagnostics in tokamak plasmas [J]. Int Conf Infra Milli, 2020.
\item XU X H, XIE J L, LIU J, LIU W D, et al. Analysis of the Anomalous Doppler Effect from Quantum Theory to Classical Dynamics Simulations [J]. Chinese Physics B,2025.
\item LI   Z H, YANG S C, XU X H, et al. A synthetic diagnostics platform for microwave imaging diagnostics in tokamaks [J]. Plasma Science and Technology, 2024, 26(3).
\item QU C M, XIE J L, ZHU Y L, XU X H, et al. The co-located arrangement of ECEI and MIR microwave imaging diagnostics on EAST tokamak [J]. Journal of Instrumentation, 2023, 18(10).
\item QU C M, XIE J L, XU X H, et al. Experimental observation of micro-tearing modes in the tokamak pedestal [J].Radiation Effects and Defects in Solids, 2023, 179(3-4).
\item HAN D Q, XIE J L, HUSSAIN A, Xu X H,et al. In situ relative self-dependent calibration of electron cyclotron emission imaging via shape matching [J]. Review of Scientific Instruments, 2018, 89(10).
\item GAO B X, XIE J L, ZHAO Z L, Xu X H,et al. Diagnostic capacity of electron cyclotron emission imaging system with continuous large observation area on EAST tokamak [J]. Review of Scientific Instruments, 2018, 89(9).
\item
LIAO W, GAO F, XU X, et al. Bench test of microwave imaging reflectometry system for EAST tokamak [J]. Journal of Instrumentation, 2020, 15(03): C03036.
\item
高飞雪, 刘贤子, 渠承明,徐新航, et al. EAST 装置微波反射成像系统光学性能评测 [J]. 核聚变与等离子体物理, 2022, 42(2): 187.
%\item YU G Y, XIE J L, XU X H, et al. Modelling of the electron cyclotron emission burst from a laboratory tokamak plasma with loss-cone maser instability [J]. Journal of Plasma Physics, 2024, 90(6).
%\item  LUO C, TANG X P, XU X H, et al. Design of a 170GHz quasi-optical notch filter for microwave-based diagnostics protection on the burning plasma device [J]. Fusion Engineering and Design, 2025, 214.
%\item LI X L, ZHU Y L, XU X H, et al. System-on-chip technology application on microwave imaging reflectometer [J]. Plasma Physics and Controlled Fusion, 2025, 67(5).
%\item SUN P J, LI X L, XU X H, et al. Development and preliminary results of 270 GHz microwave forward scattering diagnostic system on the experimental advanced superconducting tokamak (EAST) [J]. Plasma Physics and Controlled Fusion, 2025, 67(8).
%\item LIU X Z, REN Y, XU X H, et al. High-wavenumber Collective Scattering Diagnostic System for EAST and NSTX-U Tokamaks and Synthetic Diagnostic System Development [J]. APS Division of Plasma Physics Meeting Abstracts, 2024, 2024
\end{enumerate}

@@

\begin{enumerate}
\item Xu Xinhang, Xie Jinlin, et al.Constraining Electron Energy in static electric Field via the Anomalous Doppler Resonant with External Electromagnetic Waves.
\item Xu Xinhang, Xie Jinlin, et al.Trapping analysis of a magnetic electron by a circularly polarized electromagnetic wave in static electric field.
%\item XU Xinhang, et al. Optimization and Active Stabilization of a Far-Infrared Laser for NSTX-U High Poloidal Wavenumber Scattering Diagnostics.
%\item XU Xinhang, et al. Influence of the Cotton–Mouton Effect on Interferometric Measurements in the NSTX Tokamak with Sheared Magnetic Fields.
\end{enumerate}
